### 2023-05-03 chapter2/chapter2.tex
Added new citation for motifs acting as switches

This form of selective constraint can also describe the evolution of more ``localized'' features in IDRs such as short linear motifs (SLiMs). Because SLiMs are composed of fewer than 12 residues, they form limited interfaces that frequently mediate the transient binding events involved in signaling pathways~\cite{Tompa2014}. Accordingly, they are highly enriched in IDRs, which provide an accessible and flexible scaffold for these interactions~\cite{Fuxreiter2007, Davey2012}. While some SLiMs in IDRs are strongly conserved at specific positions, these constitute a small fraction of disordered residues, estimated at roughly 17\% in the yeast proteome~\cite{NguyenBa2012}. Instead, as SLiMs are compact and often highly degenerate at some positions, they can arise de novo from a small number of mutations and therefore have high rates of turnover. Furthermore, when IDRs contain multiple copies of a motif that jointly mediate a high-avidity interaction~\cite{Tompa2014} or a graded response to a signal via the accumulation of multiple phosphorylations~\cite{Wright2014}, the individual motifs are under weak selective constraints. As a result, though SLiMs are encoded by specific sequences, in some contexts they may evolve as distributed features that characterize IDRs as a whole rather than specific sites within them~\cite{Tan2010}.

>>>>

This form of selective constraint can also describe the evolution of more ``localized'' features in IDRs such as short linear motifs (SLiMs). Because SLiMs are composed of fewer than 12 residues, they form limited interfaces that frequently mediate the transient binding events involved in signaling pathways~\cite{Tompa2014}. Accordingly, they are highly enriched in IDRs, which provide an accessible and flexible scaffold for these interactions~\cite{Fuxreiter2007, Davey2012}. While some SLiMs in IDRs are strongly conserved at specific positions, these constitute a small fraction of disordered residues, estimated at roughly 17\% in the yeast proteome~\cite{NguyenBa2012}. Instead, as SLiMs are compact and often highly degenerate at some positions, they can arise de novo from a small number of mutations and therefore have high rates of turnover. Furthermore, when IDRs contain multiple copies of a motif that jointly mediate a high-avidity interaction~\cite{Tompa2014} or a graded response to a signal via the accumulation of multiple phosphorylations~\cite{VanRoey2012, Wright2014}, the individual motifs are under weak selective constraints. As a result, though SLiMs are encoded by specific sequences, in some contexts they may evolve as distributed features that characterize IDRs as a whole rather than specific sites within them~\cite{Tan2010}.
